Output Summary

### 2021-08-31 03-post-process/output-plots.Rmd
Include data uncertainty in survival fit plots

```{r summer-surv-fit, fig.width = 6, fig.height = 5}
plot_f = function(j) {
  plot_tseries(post_summ(post, sub_index("^phi_Pb_Ma[.+,pop]", pop = j)), expit(jags_data$Lphi_obs_Pb_Ma[observable,j]), main = pops[j])
}

@@

```{r fall-surv-fit, fig.width = 6, fig.height = 5}
plot_f = function(j) {
  plot_tseries(post_summ(post, sub_index("^phi_Pa_Ma[.+,LH_type,pop]$", LH_type = i_fall, pop = j)), expit(jags_data$Lphi_obs_Pa_Ma[observable,i_fall,j]), main = pops[j])
}

@@

```{r spring-surv-fit-nor, fig.width = 6, fig.height = 5}
plot_f = function(j) {
  plot_tseries(post_summ(post, sub_index("^phi_Mb_Ma[.+,LH_type,origin,pop]$",LH_type = i_spring, origin = o_nor, pop = j)), expit(jags_data$Lphi_obs_Mb_Ma[observable,i_spring,o_nor,j]), main = pops[j])
}

@@

```{r spring-surv-fit-hor, fig.width = 6, fig.height = 5}
plot_f = function(j) {
  plot_tseries(post_summ(post, sub_index("^phi_Mb_Ma[.+,LH_type,origin,pop]$", LH_type = i_spring, origin = o_hor, pop = j)), expit(jags_data$Lphi_obs_Mb_Ma[observable,i_spring,o_hor,j]), main = pops[j])
}

@@

```{r hydro-nor-surv-fit, fig.width = 6, fig.height = 5}
par(oma = c(1.5,1.5,0,0))
plot_tseries(post_summ(post, sub_index("^phi_Ma_O0[.+,origin]$", origin = o_nor)), expit(jags_data$Lphi_obs_Ma_O0[observable,o_nor]), main = TeX("$LGR\\,Smolt \\rightarrow O_0\\,Survival\\,(NOR)"))
mtext(side = 1, outer = T, line = 0.25, "Brood Year")
mtext(side = 2, outer = T, line = 0.25, "Survival")
```

@@

```{r hydro-hor-surv-fit, fig.width = 6, fig.height = 5}
par(oma = c(1.5,1.5,0,0))
plot_tseries(post_summ(post, sub_index("^phi_Ma_O0[.+,origin]$", origin = o_hor)), expit(jags_data$Lphi_obs_Ma_O0[observable,o_hor]), main = TeX("$LGR\\,Smolt \\rightarrow O_0\\,Survival\\,(HOR)"))
mtext(side = 1, outer = T, line = 0.25, "Brood Year")
mtext(side = 2, outer = T, line = 0.25, "Survival")
```

>>>>

```{r summer-surv-fit, fig.width = 6, fig.height = 5}
plot_f = function(j) {
  plot_tseries(post_summ(post, sub_index("^phi_Pb_Ma[.+,pop]", pop = j)),
               get_obs_ests_logit_normal(jags_data$Lphi_obs_Pb_Ma[observable,j], jags_data$sig_Lphi_obs_Pb_Ma[observable,j]),
               main = pops[j])
}

@@

```{r fall-surv-fit, fig.width = 6, fig.height = 5}
plot_f = function(j) {
  plot_tseries(post_summ(post, sub_index("^phi_Pa_Ma[.+,LH_type,pop]$", LH_type = i_fall, pop = j)),
               get_obs_ests_logit_normal(jags_data$Lphi_obs_Pa_Ma[observable,i_fall,j], jags_data$sig_Lphi_obs_Pa_Ma[observable,i_fall,j]),
               main = pops[j])
}

@@

```{r spring-surv-fit-nor, fig.width = 6, fig.height = 5}
plot_f = function(j) {
  plot_tseries(post_summ(post, sub_index("^phi_Mb_Ma[.+,LH_type,origin,pop]$",LH_type = i_spring, origin = o_nor, pop = j)),
               get_obs_ests_logit_normal(jags_data$Lphi_obs_Mb_Ma[observable,i_spring,o_nor,j], jags_data$sig_Lphi_obs_Mb_Ma[observable,i_spring,o_nor,j]),
               main = pops[j])
}

@@

```{r spring-surv-fit-hor, fig.width = 6, fig.height = 5}
plot_f = function(j) {
  plot_tseries(post_summ(post, sub_index("^phi_Mb_Ma[.+,LH_type,origin,pop]$", LH_type = i_spring, origin = o_hor, pop = j)),
               get_obs_ests_logit_normal(jags_data$Lphi_obs_Mb_Ma[observable,i_spring,o_hor,j], jags_data$sig_Lphi_obs_Mb_Ma[observable,i_spring,o_hor,j]),
               main = pops[j])
}

@@

```{r hydro-nor-surv-fit, fig.width = 6, fig.height = 5}
par(oma = c(1.5,1.5,0,0))
plot_tseries(post_summ(post, sub_index("^phi_Ma_O0[.+,origin]$", origin = o_nor)),
             get_obs_ests_logit_normal(jags_data$Lphi_obs_Ma_O0[observable,o_nor], jags_data$sig_Lphi_obs_Ma_O0[observable,o_nor]),
             main = TeX("$LGR\\,Smolt \\rightarrow O_0\\,Survival\\,(NOR)"))
mtext(side = 1, outer = T, line = 0.25, "Brood Year")
mtext(side = 2, outer = T, line = 0.25, "Survival")
```

@@

```{r hydro-hor-surv-fit, fig.width = 6, fig.height = 5}
par(oma = c(1.5,1.5,0,0))
plot_tseries(post_summ(post, sub_index("^phi_Ma_O0[.+,origin]$", origin = o_hor)),
             get_obs_ests_logit_normal(jags_data$Lphi_obs_Ma_O0[observable,o_hor], jags_data$sig_Lphi_obs_Ma_O0[observable,o_hor]),
             main = TeX("$LGR\\,Smolt \\rightarrow O_0\\,Survival\\,(HOR)"))
mtext(side = 1, outer = T, line = 0.25, "Brood Year")
mtext(side = 2, outer = T, line = 0.25, "Survival")
```
